\Large{Adversarial Training against Systematic Uncertainty}

### 2016-09-29 tex/paper.tex
save

In high energy physics, systematic uncertainties represent our incomplete
knowledge in the simulation of physical processes or in the properties of the
detection apparatus. In effect, these uncertainties typically cause variations
in the conditional distributions of the data, thereby altering the decisions and
resulting efficacy of a classifier trained from it. To accomodate for this, we
repurpose adversarial training as a means to learn a pivotal classifier which is
invariant to variations of the nuisance parameters describing the effects of
systematic uncertainties. In particular, we show and derive theoretical
conditions under which classification optimality and invariance with respect to
systematics can be achieved, which we confirm experimentally on a couple of
illustrative examples. In machine learning, this problem is closely related to
those of domain adaptation and enforcing fairness in classification. Following
that line of work, the proposed method can be regarded as generalization that
also supports the continuous case, which can be viewed as handling infinitely
many domains or as enforcing fairness over continuous features.

>>>>

In high energy physics, systematic uncertainties represent our incomplete
knowledge in the theory of physical processes or in the properties of the
experimental detection apparatus. In effect, these uncertainties typically cause
variations in the conditional distributions of the data, thereby altering the
decisions and resulting efficacy of a classifier trained from it. To contain
this issue, we propose to repurpose adversarial training as a means to learn a
pivotal classifier which is invariant to variations of the nuisance parameters
describing the effects of systematic uncertainties. In particular, we show and
derive theoretical conditions under which classification optimality and
invariance with respect to systematics can be achieved, which we confirm
experimentally on a couple of illustrative examples. In machine learning, this
problem is closely related to those of domain adaptation and enforcing fairness
in classification. Following that line of work, the proposed method can be
regarded as generalization that also supports the continuous case, which can be
viewed as handling infinitely many domains or as enforcing fairness over
continuous features.
